
---
title: "Can we get good estimates of weird quantities by using a bunch of people's guesses?"
output: html_notebook
---

Last updated: `r format(Sys.time(), "%B %d, %Y, %H:%m %Z")`

## Context
Questions were given in groups of nine. There were 4 groups. We're only looking at groups A, B, and C here, holding D out
to see if our conclusions give us good out-of-sample predictions.

## The questions
```{r, echo = FALSE, results = "asis"}
knitr::kable(questions_output_table) %>%
  kableExtra::kable_styling(bootstrap_options = "striped")
```

The short names are used throughout the rest of this document.  

## The guesses

```{r, echo=FALSE, message=FALSE, warning=FALSE, include=TRUE, fig.width=14, fig.height=30, dpi = 300}
facetted_histogram_plot
```



It's common for the mean guess to be far from the true value, because of one crazy-high guess. Examples: President age; Big Mac calories; Harry Potter words; Elevators. (Counter-examples: Yellowstone visitors; LEGOs). So the median is the better average to take. 